---
title: "Homework 01: Getting Setup"
output: html_document
---

Due date: 2017-01-27

1. Download and install [R](https://www.r-project.org/) and then [RStudio](https://www.rstudio.com/).  Then install some packages in R, using the following code.

```{r, eval=FALSE}
install.packages(c("tidyverse", "ape")) # copy and paste this line
```

Here's an example of loading an R package,

```{r, eval=FALSE}
library(tidyverse)
```

Ensure these two R packages are properly installed by loading each, very little should happen, but mainly no errors should occur.

2. Pretend you are interested in the following and provide a reasonable statement about some potential difficulties of randomly sampling
  - Ashley Madison user characteristics;
  - average inflation pressure of Tom Brady's game time footballs;
  - average weight of U.S.\ children's goldfish.

3. For the three examples in 2., state what variable type would be observed and what statistic(s) might be of interest.

3. Identify two possible lurking variable that might affect Tom Brady's game time football inflation pressure.