---
title: "Homework 04"
output: html_document
---

Due date: 2016-10-07

1. Assume you obsvered $X_1, \ldots, X_n \sim_{iid} Exp(\lambda)$.
    a. Simulate the above scenario in R by generating n random variables that follow the exponential distribution with parameter $\lambda$ -- choose $\lambda$ to generate the data and then pretend you don't know the value until you check your work.
    b. Find the MLE for $\lambda$ via calculus and compute this value in R.
    c. Find the MLE for $\lambda$ via R's function optim.
    d. Compare your answers to the values returned by the functions mean.

1. The histogram below shows the distribution of ages of pennies at a bank.
    a. Describe the distribution.
    b. Sampling distributions for means from simple random samples of 5, 10, and 100 pennies is shown in the histograms below. Describe the shapes of these distributions and comment on whether they look like what you would expect to see based on the Central Limit Theorem.
    c. The mean age of the pennies is 10.44 years, with a standard deviation of 9.2 years. Using the Central Limit Theorem, calculate the means and standard deviations of the distribution of means from random samples of size 5, 30, and 100. Comment on whether the sampling distributions shown in part (b) agree with the values you compute.

```{r, include=FALSE}
library(tidyverse)
pennies <- read_rds("pennies.Rds")
```

```{r, echo=FALSE, fig.width=4, fig.height=3, align="center"}
qplot(age, data=pennies, geom="histogram", binwidth=5, main="Distribution of ages of pennies")
```

```{r, echo=FALSE, fig.width=3, fig.height=2.5, fig.show="hold", cache=TRUE}
R <- 5000
Rs <- 1:R
xbar <- rep(NA, R)
idx <- 1:nrow(pennies)
for(i in Rs) {
    sub <- sample(idx, size=5, replace=TRUE)
    xbar[i] <- mean(pennies$age[sub])}
qplot(xbar, geom="histogram", binwidth=2, xlab=expression(bar(X)[5]))
for(i in Rs) {
    sub <- sample(idx, size=10, replace=TRUE)
    xbar[i] <- mean(pennies$age[sub])}
qplot(xbar, geom="histogram", binwidth=1, xlab=expression(bar(X)[10]))
for(i in Rs) {
    sub <- sample(idx, size=100, replace=TRUE)
    xbar[i] <- mean(pennies$age[sub])}
qplot(xbar, geom="histogram", binwidth=0.5, xlab=expression(bar(X)[100]))
```

2. A housing survey was conducted to determine the price of a typical home in Topanga, CA. The mean price of a house was roughly $1.3 million with a standard deviation of $300,000. There were no houses listed below $600,000 but a few houses above $3 million.
    a. Is the distribution of housing prices in Topanga symmetric, right skewed, or left skewed?
    b. Would you expect most houses in Topanga to cost more or less than $1.3 million?
    c. Can we estimate the probability that a randomly chosen house in Topanga costs more than
$1.4 million using the normal distribution?
    d. What is the probability that the mean of 60 randomly chosen houses in Topanga is more than $1.4 million?
    e. How would doubling the sample size affect the standard deviation of the mean?

3. Each year about 1500 students take the introductory statistics course at a large university. This year scores on the final exam are distributed with a median of 74 points, a mean of 70 points, and a standard deviation of 10 points. There are no students who scored above 100 (the maximum score attainable on the final) but a few students scored below 20 points.
    a. Is the distribution of scores on this final exam symmetric, right skewed, or left skewed?
    b. Would you expect most students to have scored above or below 70 points?
    c. Can we calculate the probability that a randomly chosen student scored above 75 using the normal distribution?
    d. What is the probability that the average score for a random sample of 40 students is above 75?
    e. What is the probability that the average score for a random sample of 80 students is above 75?